Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-20 paper/ijcai/paper.tex
small changes

% \author{
% First Author$^1$,
% Second Author$^2$,
% \\
% $^1$ First Affiliation\\
% $^2$ Second Affiliation\\
% %
% first@email.address,
% second@email.address,
% third@email.address
% }

% If your authors do not fit in the default space, you can increase it
% by uncommenting the following (adjust the "2.5in" size to make it fit
% properly)
% \setlength\titlebox{2.5in}

@@

In \textbf{RQ1}, we evaluate how often \ds{} misses faulty statements, since it is one of the main problems of dynamic slicing techniques.

Table \ref{table:fsws} presents the number of faults where at least one of the faulty statements appears in the final reports of both techniques, \sfl{} and \comb{}-k.

@@

In \textbf{RQ2}, we intend to evaluate the impact of combining \ds{} to improve \ds{}.

>>>>

% Single author syntax
\author{
    Submission 6364
}
\iffalse
\author{
First Author$^1$
\and
Second Author$^2$\and
Third Author$^{2,3}$\And
Fourth Author$^4$
\affiliations
$^1$First Affiliation\\
$^2$Second Affiliation\\
$^3$Third Affiliation\\
$^4$Fourth Affiliation
\emails
\{first, second\}@example.com,
third@other.example.com,
fourth@example.com
}
\fi

@@

In \textbf{RQ1}, our concern is to evaluate how often \ds{} misses faulty statements, 
since it is one of the main issues of dynamic slicing techniques. Table \ref{table:fsws} 
presents the number of faults where at least one of the faulty statements appears 
in the final reports of both techniques, \sfl{}$^{k}$ and \combpar{k}. We only search
for faulty statements in the top $5$ ($k=5$) and $10$ ($k=10$) of the highest faulty 
classes of the projects. \combpar{k} finds the faulty statements faster than 
\sfl{}$^{k}$. Using

@@

In \textbf{RQ2}, we intend to evaluate the impact of combining \ds{} with \sfl{} to improve \ds{}.
